---
title: "Cybersecurity Risk Analysis and Simulation"
subtitle: "Simulation"
date: "`{r} Sys.Date()`"
format: pdf
params:
  pi_mag_distribution: "PERT"
  pi_event_distribution: "PERT"
  ni_nsim: 1000
  ni_event_old_min: 0
  ni_event_old_mode: 50
  ni_event_old_max: 100
  si_event_new_min: 0
  si_event_new_mode: 50
  si_event_new_max: 100
  ni_mag_old_min: 0
  ni_mag_old_mode: 5
  ni_mag_old_max: 10
  si_mag_new_min: 0
  si_mag_new_mode: 5
  si_mag_new_max: 10
  nseed: NULL
  sim_data: NULL
  simulation_time: !expr format(Sys.time(), "%Y-%m-%d %H:%M:%S")
knitr:
  opts_chunk:
    echo: false
    message: false
    warning: false
---

```{r}
#| include: false
library(cras)
library(dplyr)
library(ggplot2)
library(kableExtra)
library(plotly)
library(scales)
library(tidyr)
```

```{r}
data <- data.frame(params$sim_data)
```

## Simulation report

The simulation was run on `{r} params$simulation_time`.

### Parameters

```{r}
#| results: 'asis'

tibble(
  Parameter = c("Annual Events", "Annual Events", "Loss Magnitude per Event",
                "Loss Magnitude per Event"),
  Situation = c("Current", "Proposed", "Current", "Proposed"),
  Min = c(params$ni_event_old_min, params$si_event_new_min,
          params$ni_mag_old_min, params$si_mag_new_min),
  `Most Likely` = c(params$ni_event_old_mode, params$si_event_new_mode,
                    params$ni_mag_old_mode, params$si_mag_new_mode),
  Max = c(params$ni_event_old_max, params$si_event_new_max,
          params$ni_mag_old_max, params$si_mag_new_max)
) %>%
  knitr::kable(caption = "Input Parameters for Event Frequency and Loss
               Magnitude") |>
  kableExtra::collapse_rows(column = 1)
```

The loss magnitude distribution was a `{r} params$pi_mag_distribution`, the loss
event frequency distribution was a `{r} params$pi_event_distribution` and the simulation was run for `{r} params$ni_nsim` iterations.
This simulation `{r} ifelse(is.null(params$nseed), "didn't use a seed", paste("used the seed", params$nseed))`.

### Loss Magnitude

This plot shows the density distribution of loss magnitude in the simulation.

```{r}
#| fig-height: 4
#| fig-width: 4
#| fig-align: 'center'
#| out-width: "60%"
#| fig.cap: "Magnitude density plot"
cras::plot_densities(data, loss_type = "magnitude")
```

This graph shows the annualized Loss Exceedance Chart (LEC), which represents the probability of exceeding different loss amounts.

```{r}
#| fig-height: 4
#| fig-width: 4
#| fig-align: 'center'
#| out-width: "60%"
#| fig.cap: "Annualized Loss Exceedance Chart (LEC)"
cras::plot_chance(data, loss_type = "magnitude")
```

### Loss Events Frequency

This plot shows the density distribution of loss events in the simulation, which means the amount of years in which each possible amount of events is observed.

```{r}
#| fig-height: 4
#| fig-width: 4
#| fig-align: 'center'
#| out-width: "60%"
#| fig.cap: "Amount of years per amount of events"
cras::plot_densities(data, loss_type = "events")
```

### Probability of Exceeding Loss Events

This plot shows the probability of exceeding different amount of events in the simulation.

```{r}
#| fig-height: 4
#| fig-width: 4
#| fig-align: 'center'
#| out-width: "60%"
#| fig.cap: "Annualized chance of exceeding loss events"
cras::plot_chance(data, loss_type = "events")
```
